---
title: House Prices - Advanced Regression Techniques"
output: html_notebook
---

load the required packages first

```{r}
library(mlr,quietly = TRUE)
library(dplyr,quietly = TRUE)
library(ggplot2,quietly = TRUE)
library(caret,quietly = TRUE)
library(purrr,quietly = TRUE)
library(data.table,quietly = TRUE,warn.conflicts = FALSE)
library(readr,quietly = TRUE,warn.conflicts = FALSE)
```

Load the test and train datasets

```{r}
train=read_csv("train.csv")
test=read_csv("test.csv")
```

Rbind the two datasets to perform feature engineering, will later separate the two datasets again. Remove the variable Sale Price from the training set

```{r}
SalePrice=train$SalePrice
train$SalePrice=NULL
train_test=rbind(train,test)
```

Find the str of the combined train_test dataset. Also take the summary

```{r}
str(train_test)
summary(train_test)
```

Take all 'Character' class types and convert to factor (categorical) types

```{r}
trn_tst_chr=train_test %>% 
  select_if(is.character) %>% 
  mutate_each(funs(as.factor))
str(trn_tst_chr)
```

find the number of NAs in each of the factor variables

```{r}
colSums(sapply(trn_tst_chr,is.na))
```

Variables Alley, FireplaceQu, PoolQC, Fence, MiscFeature have very high NAs and are removed

```{r}
trn_tst_chr$Alley=NULL
trn_tst_chr$FireplaceQu=NULL
trn_tst_chr$PoolQC=NULL
trn_tst_chr$Fence=NULL
trn_tst_chr$MiscFeature=NULL
# rerun the command for finding total NAs in the factor variables
colSums(sapply(trn_tst_chr,is.na))
```

Perform imputation of missing factor levels using mode. Use 'Impute' function from mlr package 

```{r}
imp_fctr=impute(trn_tst_chr,classes = list(factor=imputeMode()))
colSums(sapply(imp_fctr$data,is.na))
trn_tst_chr=imp_fctr$data
head(trn_tst_chr,10)
str(trn_tst_chr)
#no missing values now
```

Take all numerics variables separately 

```{r}
str(train_test)
fac_cols=colnames(trn_tst_chr)
trn_tst_num=sapply(train_test,is.numeric)
trn_tst_numeric=train_test[,trn_tst_num]
```

Find the number of NAs in the numeric variables

```{r}
colSums(sapply(trn_tst_numeric,is.na))
```

There are not too many columns with many NAs. We can impute the missing values by a measure of centrality - mean or median. 

```{r}
imp_num=impute(trn_tst_numeric,classes = list(integer=imputeMedian()))
imp_num$desc
head(imp_num$data,10)
# again find the total NAs in each variable
colSums(sapply(imp_num$data,is.na))
trn_tst_numeric=imp_num$data
# no NAs left in the model
```

Separate out the date (year variables) from the numerics variables, also separate out the ID variable

```{r}
names(trn_tst_numeric)
trn_test_dat=trn_tst_numeric[,c(1,7,8,26,36,37)]
#Remove these variables from the trn_tst_numeric dataset
trn_tst_numeric=trn_tst_numeric[,-c(1,7,8,26,36,37)]
```

Check and remove any constant features (min variation) as they don't help in machine learning, The percentage of variabilitiy is kept at 5% meaning all features with below 5% variability are removed

```{r}
trn_tst_numeric=removeConstantFeatures(trn_tst_numeric,perc = 0.05)

```

5 variables with low variance were removed. 

Next visualize intra feature correlation. Load package corrplot

```{r}
library(corrplot)

numcorr=cor(trn_tst_numeric)
corrplot(numcorr)
```

Find variables of high correlation with each other (multicollinearity) and remove them. Use findCorrelation function from Caret package. All variables with more than 65% correlation are flagged and removed

```{r}
library(DMwR)

highcorvar=findCorrelation(numcorr,cutoff = 0.65)
# 4 Variables have high multicollinearity
names(trn_tst_numeric[,highcorvar])
trn_tst_numeric=trn_tst_numeric[,-highcorvar]
```

combine numeric, factor and date datasets back together using cbind, remove other datasets that are no longer needed

```{r}
train_test_mod=cbind(trn_test_dat,trn_tst_numeric,trn_tst_chr)
sum(is.na(train_test_mod))
#no missing values
rm(trn_test_dat,trn_tst_chr,trn_tst_num,trn_tst_numeric,train_test,numcorr,highcorvar,imp_fctr,imp_num,YearBuilt)

```

Separate out the train and test sets. Add the response variable 'SalePrice back to training dataset

```{r}
mod_train=train_test_mod[1:1460,]
mod_test=train_test_mod[1461:nrow(train_test_mod),]
mod_train$SalePrice=SalePrice
```

